---
title: "EDAV -Investing"
author: 'Animesh Verma(uni : av2354)'
date: "December 5, 2018"
output:
  html_document: default
  pdf_document: default
header-includes: \usepackage{color}
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, message=FALSE, warning=FALSE}
library("Rblpapi")
con <- blpConnect()
library(rmarkdown);
library("tidyquant")
library("quantmod")
library("dplyr")
library("tidyverse")
library("ggplot2")
library("Rblpapi")
library(gridExtra)
library(grid)
```

 
```{r, message=FALSE, warning=FALSE}
Asset_Class_Levels<-c('VWELX US Equity','LBUSTRUU INDEX','SPX INDEX') %>%
     tq_get(get         = "Rblpapi",
            rblpapi_fun = "bdh",
            fields      = c("PX_LAST"),
            options     = c("periodicitySelection" = "QUARTERLY"),
            from        = "1979-12-31",
           to          = "2015-12-31")


Asset_Class_Levels<-as.data.frame(Asset_Class_Levels) 
summary(Asset_Class_Levels)
Asset_Class_Rtns_v1<-Asset_Class_Levels %>% group_by(symbol) %>% tq_transmute(select = PX_LAST, mutate_fun =
periodReturn, period= "quarterly", type = "log",col_rename ="quarterly.returns")
Asset_Class_Rtns_v1<-as.data.frame(Asset_Class_Rtns_v1)


Asset_Class_Rtns_v1%>%group_by(symbol)%>%tq_mutate(mutate_fun =rollapply,width=4,FUN=sum,by.column=FALSE, col_rename=c("Rolling_One_Yr"))

rol1yr<-Asset_Class_Rtns_v1%>%group_by(symbol)%>%tq_mutate(mutate_fun =rollapply,width=4,FUN=sum,by.column=FALSE, col_rename=c("Rolling_One_Yr"))

rol1yr<-as.data.frame(rol1yr)
rol1yr<-rol1yr%>%filter(date>"1980-06-30")

#Data Clean 1 Year & make div adj
rol1yr$symbol[rol1yr$symbol=='SPX INDEX']<-"Stocks"
rol1yr$symbol[rol1yr$symbol=='LBUSTRUU INDEX']<-"Bonds"
rol1yr$symbol[rol1yr$symbol=='VWELX US Equity']<-"60/40 Stock/Bond"
rol1yr_DA<-rol1yr
rol1yr_DA$Rolling_One_Yr<-ifelse(rol1yr_DA$symbol=="60/40 Stock/Bond",rol1yr_DA$Rolling_One_Yr+.05,rol1yr_DA$Rolling_One_Yr)
rol1yr_DA$Rolling_One_Yr<-ifelse(rol1yr_DA$symbol=="Stocks",rol1yr_DA$Rolling_One_Yr+.025,rol1yr_DA$Rolling_One_Yr)

rol1yr_DA$symbol[rol1yr$symbol=='SPX INDEX']<-"Stocks"
rol1yr_DA$symbol[rol1yr$symbol=='LBUSTRUU INDEX']<-"Bonds"
rol1yr_DA$symbol[rol1yr$symbol=='VWELX US Equity']<-"60/40 Stock/Bond"

#Prepare 5 Year Rolling data


rol5yr<-Asset_Class_Rtns_v1%>%group_by(symbol)%>%tq_mutate(mutate_fun =rollapply,width=20,FUN=sum,by.column=FALSE, col_rename=c("Rolling_Five_Yr"))

rol5yr<-as.data.frame(rol5yr)
rol5yr<-rol5yr%>%filter(date>"1984-06-29")

#Data Clean 5 Year
rol5yr$symbol[rol5yr$symbol=='SPX INDEX']<-"Stocks"
rol5yr$symbol[rol5yr$symbol=='LBUSTRUU INDEX']<-"Bonds"
rol5yr$symbol[rol5yr$symbol=='VWELX US Equity']<-"60/40 Stock/Bond"


rol5yr_DA<-rol5yr
rol5yr_DA$Rolling_Five_Yr<-ifelse(rol5yr_DA$symbol=="60/40 Stock/Bond",rol5yr_DA$Rolling_Five_Yr+.25,rol5yr_DA$Rolling_Five_Yr)
rol5yr_DA$Rolling_Five_Yr<-ifelse(rol5yr_DA$symbol=="Stocks",rol5yr_DA$Rolling_Five_Yr+.125,rol5yr_DA$Rolling_Five_Yr)

rol5yr_DA$symbol[rol5yr$symbol=='SPX INDEX']<-"Stocks"
rol5yr_DA$symbol[rol5yr$symbol=='LBUSTRUU INDEX']<-"Bonds"
rol5yr_DA$symbol[rol5yr$symbol=='VWELX US Equity']<-"60/40 Stock/Bond"



#Prepare 10 Year Rolling data


rol10yr<-Asset_Class_Rtns_v1%>%group_by(symbol)%>%tq_mutate(mutate_fun =rollapply,width=40,FUN=sum,by.column=FALSE, col_rename=c("Rolling_Ten_Yr"))

rol10yr<-as.data.frame(rol10yr)
rol10yr<-rol10yr%>% filter(date>"1989-06-30")

#Data Clean 10 Year & Make Di Adj
rol10yr$symbol[rol10yr$symbol=='SPX INDEX']<-"Stocks"
rol10yr$symbol[rol10yr$symbol=='LBUSTRUU INDEX']<-"Bonds"
rol10yr$symbol[rol10yr$symbol=='VWELX US Equity']<-"60/40 Stock/Bond"

rol10yr_DA<-rol10yr
rol10yr_DA$Rolling_Ten_Yr<-ifelse(rol10yr_DA$symbol=="60/40 Stock/Bond",rol10yr_DA$Rolling_Ten_Yr+.5,rol10yr_DA$Rolling_Ten_Yr)
rol10yr_DA$Rolling_Ten_Yr<-ifelse(rol10yr_DA$symbol=="Stocks",rol10yr_DA$Rolling_Ten_Yr+.25,rol10yr_DA$Rolling_Ten_Yr)

rol10yr_DA$symbol[rol10yr$symbol=='SPX INDEX']<-"Stocks"
rol10yr_DA$symbol[rol10yr$symbol=='LBUSTRUU INDEX']<-"Bonds"
rol10yr_DA$symbol[rol10yr$symbol=='VWELX US Equity']<-"60/40 Stock/Bond"


#Prepare 20 Year Rolling data


rol20yr<-Asset_Class_Rtns_v1%>%group_by(symbol)%>%tq_mutate(mutate_fun =rollapply,width=80,FUN=sum,by.column=FALSE, col_rename=c("Rolling_Twnty_Yr"))

rol20yr<-as.data.frame(rol20yr)
rol20yr<-rol20yr%>% filter(date>"1999-06-30")

#Data Clean 10 Year
rol10yr$symbol[rol10yr$symbol=='SPX INDEX']<-"Stocks"
rol10yr$symbol[rol10yr$symbol=='LBUSTRUU INDEX']<-"Bonds"
rol10yr$symbol[rol10yr$symbol=='VWELX US Equity']<-"60/40 Stock/Bond"


#Data Clean 20 Year
rol20yr$symbol[rol20yr$symbol=='SPX INDEX']<-"Stocks"
rol20yr$symbol[rol20yr$symbol=='LBUSTRUU INDEX']<-"Bonds"
rol20yr$symbol[rol20yr$symbol=='VWELX US Equity']<-"60/40 Stock/Bond"


rol20yr_DA<-rol20yr
rol20yr_DA$Rolling_Twnty_Yr<-ifelse(rol20yr_DA$symbol=="60/40 Stock/Bond",rol20yr_DA$Rolling_Twnty_Yr+.9,rol20yr_DA$Rolling_Twnty_Yr)
rol20yr_DA$Rolling_Twnty_Yr<-ifelse(rol20yr_DA$symbol=="Stocks",rol20yr_DA$Rolling_Twnty_Yr+.45,rol20yr_DA$Rolling_Twnty_Yr)

rol20yr_DA$symbol[rol20yr$symbol=='SPX INDEX']<-"Stocks"
rol20yr_DA$symbol[rol20yr$symbol=='LBUSTRUU INDEX']<-"Bonds"
rol20yr_DA$symbol[rol20yr$symbol=='VWELX US Equity']<-"60/40 Stock/Bond"


#Graphing 1,5,10 and 20 year Rolling returns

g1_Rolling_One_Year<-ggplot(rol1yr_DA,aes(x=symbol,y=Rolling_One_Yr,fill=symbol))+geom_boxplot(show.legend = FALSE)+ ggtitle("1 Year Rolling Return Ranges") + scale_y_continuous(labels = scales::percent)+ xlab("Asset Class") + ylab("Rolling Annualized Return")
ggsave("g1_Rolling_One_Year.png",width=13)


g5_Rolling_Five_Year<-ggplot(rol5yr_DA,aes(x=symbol,y=Rolling_Five_Yr/5,fill=symbol))+geom_boxplot(show.legend = FALSE) +ggtitle("5 Year Rolling Return Ranges") + scale_y_continuous(labels = scales::percent)+ xlab("Asset Class")  
ggsave("g5_Rolling_Five_Year.png",width=13)


g10_Rolling_Ten_Year<-ggplot(rol10yr_DA,aes(x=symbol,y=Rolling_Ten_Yr/10,fill=symbol))+geom_boxplot(show.legend = FALSE) + ggtitle("10 Year Rolling Return Ranges") + scale_y_continuous(labels = scales::percent)+ xlab("Asset Class") + ylab("Rolling Annualized Return")
ggsave("g10_Rolling_Ten_Year.png",width=13)


g20_Rolling_Twenty_Year<-ggplot(rol20yr_DA,aes(x=symbol,y=Rolling_Twnty_Yr/20,fill=symbol))+geom_boxplot(show.legend = FALSE) + ggtitle("20 Year Rolling Return Ranges") + scale_y_continuous(labels = scales::percent)+ xlab("Asset Class") + ylab("Rolling Annualized Return") 

ggsave("g20_Rolling_Twenty_Year.png",width=13)


```


```{r, message=FALSE, warning=FALSE}
 my_bloomberg_data <- c('SPX Index') %>%
    tq_get(get         = "Rblpapi",
           rblpapi_fun = "bdh",
           fields      = c("PX_LAST"),
           options     = c("periodicitySelection" = "DAILY"),
           from        = "1995-12-31",
           to          = "2015-12-31") 
 
my_bloomberg_data<-as.data.frame(my_bloomberg_data) 
summary(my_bloomberg_data)



#Get the daily returns
SPX_Rets<-as.data.frame(diff(my_bloomberg_data$PX_LAST )/my_bloomberg_data$PX_LAST[-length(-my_bloomberg_data$PX_LAST)])
colnames(SPX_Rets)<-c("SPX Returns")
my_bloomberg_data<-my_bloomberg_data[2:nrow(my_bloomberg_data),]

my_bloomberg_data<-data.frame(my_bloomberg_data,SPX_Rets)



# Add the cumulative Retuns Column
 my_bloomberg_data<-my_bloomberg_data %>% mutate(CumRtn=cumprod(SPX.Returns+1))

  Cum_Rtn_ex_N_Days <- function(my_bloomberg_data,n){

n<-nrow(my_bloomberg_data)-n
    
test<-data.frame( my_bloomberg_data,as.data.frame(rank(my_bloomberg_data$SPX.Returns)))
colnames(test)<-c("date","PX_LAST","SPX.Returns","CumRtn","Rank")
  test %>% mutate(var=ifelse(Rank>n,0,SPX.Returns))
test1<-test %>% mutate(var=ifelse(Rank>n,0,SPX.Returns))
test2<-test1 %>% mutate(CumRtn_6=cumprod(var+1))
  
return(test2[nrow(test2),ncol(test2)]*1.02^20*10000)
}
 
SPX_Hist_Returns <- rbind(c("Fully Invested",Cum_Rtn_ex_N_Days(my_bloomberg_data,0)),
                          c("Missed 10 best days",Cum_Rtn_ex_N_Days(my_bloomberg_data,10)),
                          c("Missed 20 best days",Cum_Rtn_ex_N_Days(my_bloomberg_data,20)),
                          c("Missed 30 best days",Cum_Rtn_ex_N_Days(my_bloomberg_data,30)),
                          c("Missed 40 best days",Cum_Rtn_ex_N_Days(my_bloomberg_data,40)),
                          c("Missed 50 best days",Cum_Rtn_ex_N_Days(my_bloomberg_data,50)),
                          c("Missed 60 best days",Cum_Rtn_ex_N_Days(my_bloomberg_data,60))
) 
colnames(SPX_Hist_Returns)<-c("Investment", "Cumulative Growth")
SPX_Hist_Returns<-as.data.frame(SPX_Hist_Returns)


SPX_Hist_Returns$`Cumulative Growth`<-as.numeric(paste(SPX_Hist_Returns$`Cumulative Growth`))
g<-ggplot(SPX_Hist_Returns,aes(x=reorder(SPX_Hist_Returns$Investment,-SPX_Hist_Returns$`Cumulative Growth`),y=SPX_Hist_Returns$`Cumulative Growth`))+geom_col()+ ggtitle("Returns of S&P 500: \nPerformance of $10,000 investement between Jan 1996- Dec 2005")+ylab("Growth of $10K")

ggsave("g.png",width=13)



```
```{r, message=FALSE, warning=FALSE}
Asset_Class_Levels<-c('LBUSTRUU INDEX','SPX INDEX','RTY Index' ,'CPI INDX Index') %>%
     tq_get(get         = "Rblpapi",
            rblpapi_fun = "bdh",
            fields      = c("PX_LAST"),
            options     = c("periodicitySelection" = "QUARTERLY"),
            from        = "1979-12-31",
           to          = "2015-12-31")


Asset_Class_Levels<-as.data.frame(Asset_Class_Levels) 
summary(Asset_Class_Levels)
Asset_Class_Rtns<-Asset_Class_Levels %>% group_by(symbol) %>% tq_transmute(select = PX_LAST, mutate_fun =
periodReturn, period= "quarterly", type = "log",col_rename ="quarterly.returns")
Asset_Class_Rtns<-as.data.frame(Asset_Class_Rtns)

indexed_prices<-Asset_Class_Rtns%>%group_by(symbol)%>%mutate(Price_index=100*cumprod(quarterly.returns+1))

indexed_prices$symbol[indexed_prices$symbol=='SPX INDEX']<-"Large Cap Stocks"
indexed_prices$symbol[indexed_prices$symbol=='RTY Index']<-"Small Cap Stocks"
indexed_prices$symbol[indexed_prices$symbol=='CPI INDX Index']<-"Inflation"
indexed_prices$symbol[indexed_prices$symbol=='LBUSTRUU INDEX']<-"US Stocks"



Asset_growth_plot<-ggplot(indexed_prices,aes(x=date,y=Price_index,color=symbol))+geom_line()+ggtitle("Growth of hundred dollars: 1980-2015")+ylab("Growth of $100")
ggsave("Asset_growth_plot.png",width=13)
```

```{r, message=FALSE, warning=FALSE}
 
Asset_Class_Rtns%>%group_by(symbol)%>%tq_mutate(mutate_fun =rollapply,width=4,FUN=sum,by.column=FALSE, col_rename=c("Rolling_One_Yr"))

rol1yr<-Asset_Class_Rtns%>%group_by(symbol)%>%tq_mutate(mutate_fun =rollapply,width=4,FUN=sum,by.column=FALSE, col_rename=c("Rolling_One_Yr"))

rol1yr<-as.data.frame(rol1yr)
rol1yr<-rol1yr%>%filter(date>"1980-06-30")

g1<-ggplot(rol1yr,aes(x=symbol,y=Rolling_One_Yr)) + geom_boxplot()
g10<-ggplot(rol10yr,aes(x=symbol,y=Rolling_Ten_Yr/10)) + geom_boxplot()


```

## Investing

Invest for long-term growth potential and consider investing in a broader mix of assets. Financial risks
don't end when careers do. Individuals planning for a long, rewarding retirement must anticipate and
overcome the obstacles that are likely to arise along the way.

### Common Misconceptions

*"The market is too volatile. I'm going to sit on the sidelines for a bit so I don't lose money."*


- Don't avoid investing in volatile times. It can cause you to miss out on potential market rallies. 

- Set specific retirement goals upfront-and keep focused on the long term during periods of volatility
and uncertainty. 


*"I should invest conservatively so I don't run the risk of losing my retirement assets."*


- Retirement-age investors have potentially long time horizons, due to rising life expectancies.
By maintaining an exposure to equities in retirement, you may better keep pace with rising prices,
protecting your standard of living throughout retirement. 


- A well-diversified portfolio may provide a smoother ride over the long term. 



## Goals based Wealth management

### Divide and Conquer

- Aligning your investment strategy by goal can help you take different levels of risk based on varying time horizons and make sure you are saving enough to accomplish all of your goals-not just the ones that occur first.



```{r, message=FALSE, warning=FALSE}
grid.arrange(g1_Rolling_One_Year,g5_Rolling_Five_Year,g10_Rolling_Ten_Year,g20_Rolling_Twenty_Year)

```

- We can see from the above chart, that over longer terms(>5 years), return of risky assets
are almost always positive and cash is no substitute.


### Impact of being out of market. 

-Trying to time the market is extremely difficult. Market lows often result in emotional decision making. Investing for the long term while managing volatility can result in a better retirement outcome

-Six of the 10 best days occured within two weeks of the 10 worst days


```{r pressure, echo=FALSE}
g + xlab("") +ylab("Growth of $10,000") + coord_flip()
```

##Major asset classes vs. inflation

- Cash may not be an effective long-term solution
```{r, message=FALSE, warning=FALSE}
Asset_growth_plot 

```